Projit: An Open Source tool for Decoupled Data Science

### 2024-11-08 docs/paper/escience/paper.tex
Clean up docs/paper folder for JOSS submission

Software approaches to managing data, processes and meta-data are typically referred to 
as e-science platforms. In general they are either build for specific scientific domains
\cite{Howe2008,} or they are designed for very specific technology stacks (common in a given domain)
\cite{Subramanian2013}.

>>>>

Software approaches to managing scientific data, processes and meta-data are typically referred to 
as e-science platforms. In general they are either built as front-ends for specific 
scientific domains \cite{Howe2008,Pettit:2010} (leveraging known analytical practices in
the given domain) or they are designed to faciliate interoperability between different
technology stacks \cite{Subramanian2013}. Machine learning focused frameworks tend to 
focus on solving problems of model training and deployment for specific technologies\cite{Alberti:2018,MolnerDomenech:2020}, and hence have limited generality.
